---
title: "Culture in Crisis | SocKult exam F24"
author: "Naja Mølle Lindelof"
date: "2024"
output:
  pdf_document: default
  html_document: default
---

# Install packages and set up coding environment

LINK FOR IMPLEMENTING RENV FOR REPRODUCIBILITY:
https://raps-with-r.dev/repro_intro.html

Using the following package versions:
- Base R 4.3.2
- pacman 0.5.1
- tidyverse 2.0.0
- tidytext 0.4.2
- topicmodels 0.2.16
- tm 0.7.13
- broom 1.0.5
- scales 1.3.0
- reshape2 1.4.4
- viridis 0.6.5
- conflicted 1.2.0


```{r setup, include = F}

# Setup coding environment
knitr::opts_chunk$set(echo = TRUE)

# Use pacman package to install all the other packages
pacman::p_load(
  tidyverse, 
  tidytext, 
  topicmodels, 
  tm, 
  broom, 
  scales, 
  reshape2,
  viridis,
  conflicted
)

```



### Load preprocessed data
See preprocessing code file for details

```{r load_preprocessed}

before <- read_csv("before_final data.csv")
during <- read_csv("during_final data.csv")
after <- read_csv("after_final data.csv")

```


```{r load_tidy_data}

tidy_before <- read_csv("before_tidy data.csv")
tidy_during <- read_csv("during_tidy data.csv")
tidy_after <- read_csv("after_tidy data.csv")
tidy_all <- read_csv("all_tidy data.csv")

```

### Plot of distribution of tweets across periods

```{r distribution histogram}

# Merge original data
all_data <- bind_rows(before, during, after)

# Make a histogram of the distribution of tweets per period
all_data %>% 
  ggplot(aes(x = Datetime, fill = Period)) +
  geom_histogram(position = "identity", bins = 20, show.legend = FALSE) +
  facet_wrap(~ Period, ncol = 1) +
  # Implement colour blind friendly colour palette
  scale_fill_viridis_d() + 
  # Implement nice font
  theme(text = element_text(family = "Cambria")) +
  ggtitle("Distribution of tweets across periods")

```


## NLP: Topic modelling

### Convert data to DTM
For many machine learning algorithm, it is necessary to convert data to the format document-term matrix (DTM), a common matrix format representing tokens (the semantic units) as columns, documents (i.e. the tweets) as rows, and term frequency (number of times a token appears in a document) as the matrix values. As most term-document pairings will not occur at all (then the documents, i.e. tweets, would be nearly identical), many term frequency values will be 0; the amount of zero-values is the _sparsity_ of the matrix.


```{r dtm_fuction}

# Build function for converting the tidy data frames containing the tokens to DTMs
dtm_data <- function(tidy_data){
  grouped_data <- tidy_data %>% 
    
    # Remove the two keywords used to scrape the data due to their naturally occuring high frequency
      # Note that I keep the third keyword, kulturpolitik, because it is meaningful for the following analysis
    dplyr::filter(word != "#dkpol", word != "#dkkultur") %>%

  # Assuming no equal datetimes in the format (Y-M-D H:M:S):
    # Reassemble the token words into their original tweets using their datetimes
    group_by(Datetime) %>% 
    mutate(Text = paste(word, collapse = " ")) %>% 
    
    # Clean up in output: Keep only one version of reassembled tweets, discard tidy words column
    ungroup() %>% 
    distinct(Datetime, .keep_all = T) %>%
    select(-word)
  
# Make all the tweet documents into a text corpus
  corpus <- tm::Corpus(VectorSource(grouped_data$Text))
  
  # Convert this corpus to a DTM
  data_dtm <- tm::DocumentTermMatrix(corpus)
  
  return(data_dtm)
}

```

```{r dtm_of_tidy_data}

# Convert the data to DTMs using this custom function
dtm_before <- dtm_data(tidy_before)
dtm_during <- dtm_data(tidy_during)
dtm_after <- dtm_data(tidy_after)

dtm_all <- dtm_data(tidy_all)

```

### Fit LDA topic models

```{r fit_lda}

# Fit LDA topic models  
tm_before <- topicmodels::LDA(dtm_before, k = 3, control = list(seed = 1234))
tm_during <- topicmodels::LDA(dtm_during, k = 3, control = list(seed = 1234))
tm_after <- topicmodels::LDA(dtm_after, k = 3, control = list(seed = 1234))

tm_all <- topicmodels::LDA(dtm_all, k = 3, control = list(seed = 1234))

```

### Inspect topics

#### Per-topic-per-word probabilities 

```{r compute_beta}

# Compute per-topic-per-word (beta) probabilities 
topics_before <- tidytext::tidy(tm_before, matrix = "beta")
topics_during <- tidytext::tidy(tm_during, matrix = "beta")
topics_after <- tidytext::tidy(tm_after, matrix = "beta")

topics_all <- tidytext::tidy(tm_all, matrix = "beta")

```




```{r top_terms}

# Build function for finding the most common words used in each topic in a period
top_terms <- function(topics_data){
  top <- topics_data %>% 
    
    # Select the n rows of words with the highest beta-values in each topic 
    group_by(topic) %>% 
    slice_max(beta, n = 15) %>% 
    
    # Arrange these words in descending order from higher to lower beta-values for each topic
    ungroup() %>%
    arrange(topic, -beta)
  
  return(top)
}


# Build function for plotting these 
plot_top_terms <- function(top_terms){
  top_terms %>% 
    
    # Reorder the list of top terms by beta-values within to the topics to which the terms belong
    mutate(term = reorder_within(term, beta, topic)) %>%
    
    # Plot the top terms according to their beta-values
    ggplot(aes(beta, term, fill = factor(topic))) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free") +
    scale_y_reordered() +
  
    # Implement (a different) colour blind friendly colour palette  
    scale_fill_viridis_d(option = "C") +
    # and nice font:)
    theme(text = element_text(family = "Cambria"))

}

```


```{r}

# Calculate and plot top terms within each period, add period name
## Before
tt_before <- top_terms(topics_before)
ttplot_before <- plot_top_terms(tt_before) +
  ggtitle("Before")

## During
tt_during <- top_terms(topics_during)
ttplot_during <- plot_top_terms(tt_during) + 
  ggtitle("During")

## After
tt_after <- top_terms(topics_after)
ttplot_after <- plot_top_terms(tt_after) +
  ggtitle("After")

## All
tt_all <- top_terms(topics_all)
ttplot_all <- plot_top_terms(tt_all) +
  ggtitle("All periods")




# Plot the figures (not with patchwork, ruins layout:()
ttplot_before
ttplot_during
ttplot_after

ttplot_all

# Save plots using the ggsave() function
ggsave(plot = ttplot_before, file = "Before_topterms.jpeg", width = 7, height = 3.5)
ggsave(plot = ttplot_during, file = "During_topterms.jpeg", width = 7, height = 3.5)
ggsave(plot = ttplot_after, file = "After_topterms.jpeg", width = 7, height = 3.5)
ggsave(plot = ttplot_all, file = "ALL_topterms.jpeg", width = 7, height = 3.5)

```

#### Per-document-per-topic probabilities

```{r compute_gamma}

# Compute per-document-per-topic (gamma) probabilities
documents_before <- tidytext::tidy(tm_before, matrix = "gamma")
documents_during <- tidytext::tidy(tm_during, matrix = "gamma")
documents_after <- tidytext::tidy(tm_after, matrix = "gamma")

documents_all <- tidytext::tidy(tm_all, matrix = "gamma")

```




## Network analysis













